### 2011-05-31 thesis/contents.tex
Lots of text explanining how to integrate multi-novelty on the graph and how to control thresholds on it.

\section{Features}
\section{Conceptual Knowledge}
\section{Conceptual Map}

@@

\begin{equation}
\frac{P_G(x)}{P_{U a}(x)} < t_A
\end{equation}

@@

In order to give full control on the threshold on which any subset of
variables is considered novel the factor $\phi_N$ needs to be dependent on all
the $X$ variables and act as a weighting function that correctly scales the
likelihood of a given instance of the $X$ variables in order to make a
\emph{MAP} operation on the graph to yield the desired value.
Such a factor would require tunning $2^N$ parameters, describing how to
distribute the weights over all the possible $2^N$ subsets of the $X$ variables.

Aiming at feasibility a simpler approach should be used.
Requiring

This is the factor $\phi_N(X) = \prod_{i \in X} t_i$.
As so the factor $\phi_N$ can be decomposed into several $\phi_{N_i} = t_i$, one
for each variable, that measure on the threshold of detecting novelty on
the single variable $i$.

More formally, there is an interest in the new graph
Nonetheless after that a mechanism to allow to control the thresholds on
detecting novelty also needs to simple doing that the ability to control the thresholds on
variables is lost
In order to measure novelty of a set of variable the full set of approach
Aiming at obtaining a correct behaviour for detecting novelty on a certain
subset of variables
Optimally the system should re-evaluate novelty for all subsets of variables
each time new information is added.
A method to define a threshold on any subset of the $N$ variables also needs to
be introduced.

After that the system would be still be able to reason over variables on the
graph and deduce extra new novel variables if it was the case.
But such an approach would be dependent on the order of variables that the
system considers for novelty detection. And it would also suffer from inability
to reconsider the novelty on any given variable as more data becomes available.

The used approach can be extended to multiple variables. Though in order to
expand it to all the $n$ variables in the graph, $n!$ unconditional
probabilities would need to be evaluated.

Aiming at a fully probabilistic integration of novelty detection on any
number of variables the following method was introduced:

But the test to detect a given variable $a$ is novel requires both a structure
$G$ representing the case where no knowledge gaps exist and a structure $U$
representing the case where $a$ was identified as a novel class.

Such an approach would no longer be optimal and not be dynamic
executes on a new
structure $U$ 
of the semantic structure it does not allows the
semantic structure to be used

\subsection{Handling novelty signals from the low-level classifiers}
Explain how to handle novelty signals from low-level classifiers, now that we
have a model with the ability to still reason when several variables can be
novel.

>>>>

\section{Features}

\section{Conceptual Knowledge}
\section{Conceptual Map}
\label{sec:clues-from-low-level}

@@

\begin{equation}
\frac{P_G(x)}{P_{U_a}(x)} < t_A
\end{equation}

@@

\begin{figure}[h]
\centering
Yeah get a figure for here.
\caption{\label{fig:multiple-big-threshold}Factor graph extended to be able to
         represent novelty on any subset of variables. Note the added factor
         $\phi_N$ that servers as a normalization factor such that probability
         with any subset of $Y$ variables considered novel can be scaled with
         any value such that any thresholding decision mechanism can be
         implemented.}
\end{figure}

In order to give full control on the threshold on which any subset of
variables is considered novel the factor $\phi_N$ needs to be dependent on all
the $X$ variables and act as a weighting function that correctly scales the
likelihood of a given instance of the $X$ variables.
If the criterium for defining the threshold is the likelihood of all variables
$X$ being non-novel has the max likelihood if and only if
\autoref{eq:multiple-threshold} holds for all the non-empty subsets $Y$ of $X$.
The weight for $\phi_N$ when the set $Y$ is classified as novel
can be set for $t_Y$ and $\phi_N$ for the empty subset of novel variables is set
to $1$.

\begin{equation}
\label{eq:multiple-threshold}
\frac{P_G(x)}{P_{U_Y}(x)} > t_Y
\end{equation}

Still without further assumptions a threshold $t_Y$ would need to be defined for
all the $2^N-1$ non-empty subsets.
By taking a simple approach of considering the novelty on a variable independent
from the novelty on any other variable $t_Y$ can be factorized:

\begin{equation}
t_Y = \prod_{i \in Y}{t_i}
\end{equation}

This factorization yields then the interesting property to allow to split the
threshold factor $\phi_N$ into $N$ different $\phi_{N_i}$ associated with each
variable of the graph. A graph able to handle novelty detection on several
variables with the described factorization is illustrated on
\autoref{fig:multi-factorized-threshold}.

\begin{figure}[h]
\centering
Yeah get a figure for here.
\caption{\label{fig:multi-factorized-threshold}Factor graph extended to be able
         to represent novelty on any subset of variables. Note the added factor
         $\phi_N$ has been split into a $\phi_{N_i}$ still it is able to perform
         detection on multiple variables according to the factorization
         described in the text.}
\end{figure}

To sum up, the method described above allows to integrate novelty detection
into the graph, providing the agent with tools to describe its belief on the
novelty of variables on the system and to continue working with such a
representation. The mechanism is also fully probabilistic and at no time
the agent needs to take an irrevocable decision on the novelty of a variable,
allowing the agent beliefs to change over time as more data becomes available.

\subsection{Handling novelty signals from the low-level classifiers}
On \autoref{sec:clues-from-low-level} it was shown that information from the
low-level classifiers is integrated in the conceptual map in a probabilistic
way by introducing a factor $\phi_o$ on each observed variable that describes
the probabilistic distribution of that variable given by the classifier.

Since in order to detect novelty all the variables have been extended with a
new state indicating novelty. That same state can be used to integrate novelty
signals coming from the low-level classifiers.

TODO: maybe describe how those novelty signals could be generated from the
low-level classifiers\dots decision boundary distance, kernel pca, etc\dots
